Sir Alex Ferguson's Continued Tenure Could Have Only Marginal Improvements over Manchester United's EPL Performance

### 2024-04-16 paper/paper.qmd
Added Peer Review #1 recommendations.

The aim of this paper is twofold, where in the paper will first analyze the differences in performance between 2004-2013 (Sir Alex's era) and 2014-2023 (Post Sir Alex's era). Then, we will use this knowledge to build two Bayesian Models to predict and further analyze the estimand: Average League Points in each season for 2004-2013 and 2014-2023. The paper will also illustrate *how much* better Manchester United's position would have been in 2014-2023 if Sir Alex Ferguson would not have retired, helping us contribute to the debate about the greatest manager of all time.

@@

Define $y_i$ as the end-of-season league points obtained by Manchester United. Then $\beta_i$ is the win or success percentage for the season, $\gamma_i$ is the number of goals scored in the season, and $\delta_i$ is the goal difference for the season.

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i + \delta_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\delta &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
```
We run the model in R [@citeR] using the `rstanarm` package of [@rstanarm]. We use the default priors from `rstanarm`.

>>>>

The aim of this paper is twofold, where in the paper will first analyze the differences in performance between 2004-2013 (Sir Alex's era) and 2014-2023 (Post Sir Alex's era). Then, we will use this knowledge to build two Bayesian Models to predict and further analyze the **estimand**: Average League Points in each season for 2004-2013 and 2014-2023. The paper will also illustrate *how much* better Manchester United's position would have been in 2014-2023 if Sir Alex Ferguson would not have retired, helping us contribute to the debate about the greatest manager of all time.

@@

Define $y_i$ as the end-of-season league points obtained by Manchester United. Then $\beta_1$ is the win or success percentage for the season, $\gamma_1$ is the number of goals scored in the season, and $\delta_1$ is the goal difference for the season. The two models in this paper were run with auto scaling priors values for which have been obtained by running `prior_summary`. Model 1 for the time period 2004-2013 is represented as:

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i + \delta_i\\
\alpha &\sim \mbox{Normal}(0, 15) \\
\beta &\sim \mbox{Normal}(0, 2.13) \\
\gamma &\sim \mbox{Normal}(0, 1.30) \\
\delta &\sim \mbox{Normal}(0, 1.25) \\
\sigma &\sim \mbox{Exponential}(0.18)
\end{align}
```

Model 2 for the time period 2014-2023 is represented as:

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i + \delta_i\\
\alpha &\sim \mbox{Normal}(0, 16) \\
\beta &\sim \mbox{Normal}(0, 2.36) \\
\gamma &\sim \mbox{Normal}(0, 2.27) \\
\delta &\sim \mbox{Normal}(0, 1.43) \\
\sigma &\sim \mbox{Exponential}(0.15)
\end{align}
```

We run the model in R [@citeR] using the `rstanarm` package of [@rstanarm]. We use the default priors from `rstanarm`.
